|

### 2019-05-29 manuscript/article/article.tex
update manuscript

\documentclass[12pt,a4paper,]{article}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{libertine}
% If you're using libertine, this math font looks nice:
\usepackage[libertine]{newtxmath}
\usepackage[T1]{fontenc}
\usepackage[scaled=.95]{inconsolata}
% Add the following packages to support kableExtra
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{etoolbox}
% Uncomment the line below if you want to use XeLaTeX or 
% write on ShareLaTeX or Overleaf
% \setmonofont[Scale=.9,BoldFont=inconsolata-bold.ttf]{inconsolata-regular.ttf}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{setspace}
\usepackage[top=2cm,bottom=2cm,left=2.2cm,right=2.2cm]{geometry}
\usepackage[backref,pagebackref]{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{ifthen}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        Cited on page~#2.%
    \else      Cited on pages~#2.%
    \fi}
\renewcommand{\backreftwosep}{ and~} 
\renewcommand{\backreflastsep}{ and~}
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; John Meadowcroft; David Skarbek; Eugenia Guerrero},
      pdfkeywords={authoritarian regimes, Chile, georeferenced event data, Pinochet, truth
commission},
  }
\setlength{\parindent}{1cm}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{amssymb,amsmath}
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

@@

\title{\textbf{Deaths and Disappearances in the Pinochet Regime: A New Dataset}\thanks{We thank Umberto Mignozzetti and Robert Myles McDonnell for their
helpful comments. Data and replication information are available at
\href{http://github.com/danilofreire/pinochet}{\texttt{http://github.com/danilofreire/pinochet}}.}}
\author{Danilo Freire\footnote{Postdoctoral Research Fellow, the Political
  Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912,
  \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}},
  \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}.
  Corresponding author.} \and John Meadowcroft\footnote{Senior Lecturer in Public Policy, Department
  of Political Economy, King's College London,
  \href{mailto:john.meadowcroft@kcl.ac.uk}{\texttt{john.meadowcroft@kcl.ac.uk}},
  \href{http://johnmeadowcroft.net}{\texttt{http://johnmeadowcroft.net}}.} \and David Skarbek\footnote{Associate Professor, Department of Political
  Science and the Political Theory Project, Brown University,
  \href{david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}},
  \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}.} \and Eugenia Guerrero\footnote{Software Developer, Tempo UK.}}
\date{\today}

@@

\begin{abstract}
\noindent This article presents a georeferenced dataset on human rights violations
in General Augusto Pinochet's dictatorship in Chile. We manually coded
the personal details of 2,398 victims mentioned in the Chilean Truth
Commission Report and added geographical coordinates for all
identifiable atrocity locations. Our dataset comprises 57 variables from
1973 to 1990 and it is available as a stand-alone spreadsheet or as the
\texttt{pinochet} package for \texttt{R}. The data describe the
initially high-level then steep decline of human rights violations, the
extent to which the military government targeted the opposition, and the
spatial variation of state repression. We also discuss our coding
procedures, show descriptive statistics, and conclude with suggestions
for potential uses of our dataset.
\vspace{.5cm}

\noindent \textbf{Keywords}: authoritarian regimes, Chile, georeferenced event data, Pinochet, truth
commission
\vspace{.25cm}

@@

On 11 September 1973, General Augusto Pinochet led a coup against
Chile's socialist President Salvador Allende. The coup marked the
beginning of a seventeen-year military dictatorship which combined rapid
economic liberalisation with large-scale political repression
\citep{meadowcroft2014hayek, valdes1995pinochet}. In 1991, after Chile's
transition to democracy, then-President Patricio Aylwin convened a
commission to investigate human rights abuses in the Pinochet regime.
The Report of the National Commission on Truth and Reconciliation
\citeyearpar{report1991}, also known as the Rettig Report\footnote{Former
  Chilean ambassador Raúl Rettig chaired the Chilean National Commission
  for Truth and Reconciliation.}, recorded over 2,000 cases of murders
and disappearances from 1973 to 1990. The Commission confronted the
abuses of the past and portrayed a careful reconstruction of state
repression during the military government. Most important, the Report
contributed to the erosion of authoritarianism in Chile, as it fostered
a series of criminal investigations that culminated with the indictment
of General Pinochet in 2000 \citep[ 26]{brahm2007uncovering}.

Although the Report is a valuable resource to scholars, quantitative
researchers cannot readily use the rich information it contains. In this
paper, we present a manually-coded dataset with all information from the
Truth Commission Report plus new variables we collected to complement
the original data. We transcribed every personal detail from the 903
pages of the English translation of the Report, assigned a unique
identification number to each victim, then georeferenced the location of
the human rights abuses. We mapped all locations that appear in the
report, such as places used to torture, interrogate or murder the
victims.

@@

Violence during transitions has characterised regime change in Latin
America. Transitions to autocratic rule in Brazil (1964) and Argentina
(1976) prompted frequent human rights violations that only recently have
been fully documented \citep{agosin1987generals, elpais2016argentina}.
In some cases, autocrats declared unrestrained violence to be an
explicit government policy. Peru's former President Alberto Fujimori
openly stated that his \emph{autogolpe} (1992) granted him the rights to
``{[}apply{]} drastic punishments'' towards alleged terrorists
\citetext{\citealp[97]{dabene1997narcodemocracias}; \citealp[56]{samtleben2013constitucion}}.

The Pinochet regime is also notable for its brutality. On the day of the
coup, the military opened fire against the \emph{Palacio La Moneda}, the
Presidential Office, and President Salvador Allende committed suicide
after troops stormed the building \citep{verdugo2001chile}. The violence
continued during the military government. The \emph{junta} killed
thousands of students and members of labour organisations in 1973, with
up to 200,000 Chileans -- about 2\% of the country's population -- led
into exile \citep[31]{wright2007chilean}.

The establishment of the Truth and Reconciliation Commission was the
first attempt of

@@

Our dataset comprises 2,398 observations and 57 variables. Each
observation corresponds to a victim of the Pinochet regime and every
individual has a unique id number. There are several variables
describing the personal information of the victims, such as age, gender,
nationality, occupation, and political affiliation if available. The
data also feature geographical coordinates for a number of the
incidents, as well as information about methods of torture and causes of
death. Figure 01 shows an example entry from our dataset.

@@

@@

@@

As mentioned previously, our dataset includes 57 variables and covers
the seventeen years of the Pinochet Presidency (1973--1990). Figure
\ref{trend} shows the frequency of government-perpetrated incidents per
month from 1973 to 1990. We see that the majority of the acts of
violence happened in the first two months after the military coup. The
high incidence of human rights violations in the beginning of the
Pinochet era reflects the activity of the ``Caravan of Death'', a group
of paramilitaries established in October 1973 to torture and kill
dissidents
\citetext{\citealp[459]{davis1990they}; \citealp{verdugo2001chile}}.

In September 1973 alone, the government committed 633 acts of violence
against civilians, of which 406 the Commission signals as ``definite and
known deaths''. The violations continued in October, with 504 incidences
and 317 certified deaths. The numbers decline to about 10\% of those
levels in November and December, and then recede further in 1974.

@@

@@

We can further disaggregate the analysis and visualise how the regime
persecuted particular groups. Students and members of left-wing parties
are two categories of special interest. On 18 September 1073, only one
week after the coup, Pinochet and his followers rounded up thousands of
students and activists in Chile's National Stadium. Military forces
tortured and murdered hundreds of prisoners over the course of a few
days. An emblematic victim was Víctor Lidio Jara Martínez, a university
teacher, theatre director and singer (id number 25). According to
witnesses, Mr Jara had his hand crushed and his wrists broken, and he
was later shot 44 times with a machine gun. Mr Jara's body was left in
the front of the stadium as a warning for other political prisoners
\citep[ 56]{mcsherry2015victor}. The government again tortured and
killed students and activists in its campaign against the Revolutionary
Left Movement (\emph{Movimiento de Izquierda Revolucionaria}, MIR). The
MIR originated in student unions and in the late 1970s the movement
promoted a series of attacks against government personnel and official
buildings. Government forces strongly retaliated and the group resorted
to terrorist tactics to confront the regime
\citep{schlotterbeck2018beyond}.

>>>>

\documentclass[12pt,a4paper,]{article}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
\usepackage[]{libertine}
% If you're using libertine, this math font looks nice:
\usepackage[libertine]{newtxmath}
\usepackage[T1]{fontenc}
\usepackage[scaled=.95]{inconsolata}
% Add the following packages to support kableExtra
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{etoolbox}
% Uncomment the line below if you want to use XeLaTeX or 
% write on ShareLaTeX or Overleaf
% \setmonofont[Scale=.9,BoldFont=inconsolata-bold.ttf]{inconsolata-regular.ttf}
\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkblue}{rgb}{0.0,0.0,0.55}
\usepackage{setspace}
\usepackage[top=2cm,bottom=2cm,left=2.2cm,right=2.2cm]{geometry}
\usepackage[backref,pagebackref]{hyperref}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{pgf}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{positioning}
\usepackage{mathtools}
\usepackage{caption}
\usepackage{ifthen}
\usepackage[UKenglish]{babel}
\usepackage[UKenglish]{isodate}
\cleanlookdateon
\exhyphenpenalty=1000
\hyphenpenalty=1000
\widowpenalty=1000
\clubpenalty=1000
\renewcommand*{\backref}[1]{}
\renewcommand*{\backrefalt}[4]{%
    \ifcase #1 (Not cited.)%
    \or        Cited on page~#2.%
    \else      Cited on pages~#2.%
    \fi}
\renewcommand{\backreftwosep}{ and~} 
\renewcommand{\backreflastsep}{ and~}
\hypersetup{
  linkcolor=Mahogany,
  citecolor=Mahogany,
  urlcolor=darkblue, 
  breaklinks=true, 
  colorlinks=true,
      pdfauthor={Danilo Freire; John Meadowcroft; David Skarbek; Eugenia Guerrero},
      pdfkeywords={Chile, georeferenced event data, human rights, Pinochet, truth
commission},
  }
\setlength{\parindent}{1cm}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{amssymb,amsmath}
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}

@@

\title{\textbf{Deaths and Disappearances in the Pinochet Regime: A New Dataset}\thanks{We thank Umberto Mignozzetti, Lucas Mingardi and Robert Myles McDonnell
for their helpful comments. Replication materials and R source code are
available at
\href{http://github.com/danilofreire/pinochet}{\texttt{http://github.com/danilofreire/pinochet}}.}}
\author{Danilo Freire\footnote{Postdoctoral Research Fellow, the Political
  Theory Project, Brown University, 8 Fones Alley, Providence, RI 02912,
  \href{mailto:danilofreire@gmail.com}{\texttt{danilofreire@gmail.com}},
  \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}.
  Corresponding author.} \and John Meadowcroft\footnote{Senior Lecturer in Public Policy, Department
  of Political Economy, King's College London,
  \href{mailto:john.meadowcroft@kcl.ac.uk}{\texttt{john.meadowcroft@kcl.ac.uk}},
  \href{http://johnmeadowcroft.net}{\texttt{http://johnmeadowcroft.net}}.} \and David Skarbek\footnote{Associate Professor, Department of Political
  Science and the Political Theory Project, Brown University,
  \href{david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}},
  \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}.} \and Eugenia Guerrero\footnote{Software Developer, Tempo UK.}}
\date{\today}

@@

\begin{abstract}
\noindent This article presents a georeferenced dataset on human rights violations
in the Pinochet dictatorship in Chile. We coded the personal details of
2,398 victims named in the Chilean Truth Commission Report and added
geographical coordinates for all identifiable atrocity locations. The
dataset comprises 59 variables from 1973 to 1990 and is available as a
stand-alone spreadsheet or as the \texttt{pinochet} package for
\texttt{R}. As examples, we describe the major temporal and spatial
patterns of the human rights abuses. We also discuss our coding
procedures, show descriptive statistics, and conclude with suggestions
for potential applications of the dataset.
\vspace{.5cm}

\noindent \textbf{Keywords}: Chile, georeferenced event data, human rights, Pinochet, truth
commission
\vspace{.25cm}

@@

On 11 September 1973, General Augusto Pinochet led a coup against
Chile's socialist President Salvador Allende. The coup marked the
beginning of a seventeen-year military dictatorship which combined rapid
economic liberalisation with large-scale political repression
\citep{valdes1995pinochet}. In 1991, after Chile's transition to
democracy, President Patricio Aylwin convened a commission to
investigate human rights violations in the Pinochet regime. The Report
of the National Commission on Truth and Reconciliation
\citeyearpar{report1991}, also known as the Rettig Report\footnote{Former
  Chilean Senator and jurist Raúl Rettig chaired the Chilean National
  Commission for Truth and Reconciliation.}, recorded over 2,000 cases
of murders and disappearances from 1973 to 1990. The Commission
confronted the abuses of the past and portrayed a careful reconstruction
of state violence during the military government. Most importantly, the
Report contributed to the erosion of authoritarianism in Chile, as it
fostered a series of criminal investigations that culminated with the
indictment of General Pinochet in 2000 \citep[ 26]{brahm2007uncovering}.

Although the Report is a valuable source of information for scholars,
quantitative researchers cannot readily use the rich data it contains.
In this paper, we present a manually-coded dataset with all information
from the Truth Commission Report plus new variables we collected to
complement the original records. We transcribed every personal detail
from the 903 pages of the English translation of the Report, assigned a
unique identification number to each victim, then georeferenced the
location of the human rights abuses. We added coordinates of latitude
and longitude to every location mentioned in the report, such as places
used to torture, interrogate or murder the victims.

@@

Violence during transitions has characterised regime change in Latin
America. Transitions to autocratic rule in Brazil (1964) and Argentina
(1976) prompted frequent human rights violations that only recently have
been fully documented
\citep{agenciabrasil2014ditadura, elpais2016argentina}. In some cases,
autocrats declared unrestrained violence to be an explicit government
policy. In 1992, Peru's former President Alberto Fujimori openly stated
that his \emph{autogolpe} granted him the rights to ``{[}apply{]}
drastic punishments'' towards any suspect of terrorism
\citetext{\citealp[97]{dabene1997narcodemocracias}; \citealp[56]{samtleben2013constitucion}}.

The Pinochet regime was also notable for its brutality. On the day of
the coup, the military opened fire against the \emph{Palacio La Moneda},
the Presidential Office, and President Salvador Allende committed
suicide after troops stormed the building \citep{verdugo2001chile}. The
violence continued during the military government. The \emph{junta}
killed thousands of students and members of labour organisations in
1973, with up to 200,000 Chileans -- about 2\% of the country's
population -- led into exile \citep[31]{wright2007chilean}.

The establishment of the Truth and Reconciliation Commission was the
first attempt to make the dictatorship accountable for its crimes. The
Commission focused on the most serious cases of human rights violations,
which are those that resulted in deaths of disappearances\footnote{The
  Commission's mandate did not extend to cases of forced exile or
  torture that did not lead to death \citep[660]{ensalaco1994truth}.
  President Alwyn and his advisors feared the inclusion of non-lethal
  violence episodes would make the investigation unmanageable
  \citep[163]{vasallo2002truth}.}. One factor that limited the scope of
the investigations was that the Commission did not have the legal
authority to demand collaboration from the military forces
\citep[85]{popkin1995truth}. The Chilean Commission negotiated an
amnesty to perpetrator in exchange for freedom of inquiry, and it
collected testimony from victims in Chile and abroad
\citep[399]{quinn2001dealing}. The result was a broad yet accurate
description of the events. Although the military contested the
conclusions of the Report, they did not question its factual information
\citetext{\citealp[54]{bakiner2009denial}; \citealp{brahm2005beyond}}.

While the Report did not bring legal punishment to violence
perpetrators, it addressed important concerns of the victims. In
February 1992, the Chilean Congress passed a law granting a monthly
pension to individuals named in the Report, along with psychological
treatment for their families and school subsidies for their children
\citep[167]{vasallo2002truth}. The Chilean government also created a new
office to deal with returning nationals, and President Aylwin released
almost all political prisoners in the country
\citep[400]{quinn2001dealing}.

Data from the Truth Commission Report have also fostered academic
research on the effects of authoritarian violence on social outcomes.
For instance, Ensalaco
\citetext{\citeyear{ensalaco1994truth}; \citeyear{ensalaco2000chile}}
argues that the Report had a positive impact on human rights conditions
in Chile, while \citet{davis1990they} use the Report to analyse the
drivers on political violence in Chile. More recently, Esberg
\citetext{\citeyear{esberg2018antecipating}; \citeyear{esberg2018audience}}
employs data compiled from the Truth Commission Report to examine how
the Pinochet regime applied different methods of repression to appeal to
supporters and avoid political backlash.

Despite these noteworthy examples, quantitative studies on the dynamics
of authoritarian rule in Chile remains limited. We believe a major
obstacle for further research in the subject is the lack of
easily-available, pre-formatted data. Manual text coding is a
time-consuming process, and data availability would allow scholars to
investigate new aspects of the Pinochet regime.

@@

Our dataset comprises 2,398 observations and 59 variables. Each
observation corresponds to a victim of the Pinochet regime and every
individual has a unique id number. There are several variables
describing the personal information of the victims, such as age, gender,
nationality, occupation, and political affiliation if available. The
data also feature geographical coordinates for a number of the
incidents, as well as information about methods of torture and causes of
death. Table 1 shows an example entry from our dataset.

@@

\begin{table}[!h]

\caption{\label{tab:sample-obs}Sample event from the dataset (selected variables)}
\centering
\begin{tabular}{ll}
\toprule
  & Value\\
\midrule
individual\_id & 12\\
group\_id & 12\\
start\_date\_daily & 1973-09-12\\
end\_date\_daily & 1973-09-12\\
last\_name & Gojanovic Arias\\
\addlinespace
first\_name & Drago Vinko\\
minor & 0\\
age & 23\\
male & 1\\
occupation & Blue Collar\\
\addlinespace
occupation\_detail & driver at German Democratic Republic embassy\\
victim\_affiliation & Opposition\\
victim\_affiliation\_detail & Communist party\\
violence & Killed\\
method & Gun\\
\addlinespace
interrogation & NA\\
torture & NA\\
mistreatment & NA\\
targeted & NA\\
press & 0\\
\addlinespace
number\_previous\_arrests & NA\\
perpetrator\_affiliation & Regime\\
perpetrator\_affiliation\_detail & Military patrol\\
nationality & Chilean\\
place\_1 & Home\\
\addlinespace
location\_1 & Las Condes\\
latitude\_1 & -33.39901\\
longitude\_1 & -70.55731\\
exact\_coordinates\_1 & 0\\
place\_2 & In Public\\
\addlinespace
location\_2 & Intersection of Calle Tabancura and Avenida Kennedy\\
latitude\_2 & -33.38366\\
longitude\_2 & -70.53468\\
exact\_coordinates\_2 & 1\\
\bottomrule
\end{tabular}
\end{table}

\vspace{.5cm}

@@

\vspace{.5cm}

\begin{table}[!h]

\caption{\label{tab:number}Number of killings, disappearances, unresolved cases, and suicides}
\centering
\begin{tabular}{lr}
\toprule
Violence & N\\
\midrule
Disappearance & 853\\
Disappearance, Information of Death & 108\\
Killed & 1331\\
Suicide & 8\\
Unresolved & 93\\
\bottomrule
\end{tabular}
\end{table}

\vspace{.5cm}

@@

As mentioned previously, our dataset includes 57 variables and covers
the seventeen years of the Pinochet Presidency (1973--1990). Figure 1
shows the frequency of government-perpetrated incidents per month from
1973 to 1990. We see that the majority of the acts of violence happened
in the first two months after the military coup. The high incidence of
human rights violations in the beginning of the Pinochet era reflects
the activity of the ``Caravan of Death'', a group of paramilitaries
established in October 1973 to torture and kill dissidents
\citetext{\citealp[459]{davis1990they}; \citealp{verdugo2001chile}}.

In September 1973 alone, the government committed 633 acts of violence
against civilians, of which 406 the Commission signals as ``definite and
known deaths''. The violations continued in October, with 504 incidences
and 317 certified deaths. In total, the Pinochet regime made 1274
victims in its first year. The numbers decline to about 10\% of those
levels in November and December, and then recede further in 1974.

@@

\vspace{.5cm}

\begin{figure}

{\centering \includegraphics{article_files/figure-latex/time-trend-1}

}

\caption{Human rights abuses in the Pinochet regime, 1973-1990}\label{fig:time-trend}
\end{figure}

\vspace{.5cm}

@@

\begin{figure}

{\centering \includegraphics{article_files/figure-latex/maps-1}

}

\caption{Spatial variation in human rights abuses in the Pinochet regime, 1973-1990}\label{fig:maps}
\end{figure}

We can further disaggregate the analysis and visualise how the regime
persecuted particular groups. School and university students are two
categories of special interest. On 18 September 1073, only one week
after the coup, Pinochet and his followers rounded up thousands of
students and activists in Chile's National Stadium. Military forces
tortured and murdered dozens of prisoners over the course of a few days.
The government again tortured and killed students and activists in its
campaign against the Revolutionary Left Movement (\emph{Movimiento de
Izquierda Revolucionaria}, MIR). The MIR originated in student unions
and in the late 1970s the movement promoted a series of attacks against
government personnel and official buildings. Government forces strongly
retaliated and the group resorted to terrorist tactics to confront the
regime \citep{schlotterbeck2018beyond}.

\vspace{.5cm}

\begin{figure}

{\centering \includegraphics{article_files/figure-latex/time-trend-students-1}

}

\caption{Human rights abuses against students, 1973-1990}\label{fig:time-trend-students}
\end{figure}

\vspace{.5cm}
